---
title: "Rapport d'Expérience"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- readRDS("data.rds")
```

## Informations générale

**Utilisateur** : `r data$user_email`  
**Texte d'entrée** : `r data$input_txt`  
**Date de début** : `r data$experiment_date_start`  
**Date de fin** : `r data$experiment_date_end`  
**Statut** : `r data$status`  

```{r, echo=FALSE, message=FALSE, warning=FALSE}
par(mar=c(4, 4, 1, 1))
if (length(data$graph_history) > 0) {
  plot(1:length(data$graph_history), data$graph_history, type = "l", main = "Historique", xlab = "Temps", ylab = "Valeur")
}
```

## Paramètres de l'Expérience

**Puissance du laser** : `r data$laser_power` W  
**Fréquence** : `r data$frequency` Hz  
**Tension** : `r data$voltage_tension` V  
**Humidité** : `r data$humidity` %  
**Température** : `r data$temperature` °C  

## Résultats

**Résultat de l'expérience** : `r data$result_txt`  
**Rapport** : `r data$report`  
**Taux de réussite** : `r data$success_rate` %  